### 2021-09-19 plos_latex_template.tex
Rocío: Editing rule 9 financial

If the conference is in person, the venue must be accessible for people with mobility limitations. 
Accommodations such as a quiet space for neurodivergent people should also be provided.
Presenters should always speak into a microphone to make it easier for the hard of hearing and for captioners or interpreters to listen to them. 
Regardless of the conference format --online, in person, or hybrid --images used in communications about the conference should be accompanied by alternative text, while videos should have both captions and sound. Do not forget about art shows and movies when making sure that the materials presented are accessible for all. 
Platforms for conference registration and abstract submission, websites, and chat platforms --if used --should be screen-reader friendly and keyboard accessible, with low technology requirements (hardware, software, and internet connection). 
Captioning for presentations should be available in more than one language if possible.
These aspects should be tested well in advance of going live.

@@

\section{Express this welcoming spirit in your communication strategy}
\label{rule_communication}
%ast: sara mentioned something that can be good spirit for the communication rule: don't do anything to the outside that you are not doing for your team. it's communication strategy but also there should be coherence between your actions and your words.

@@

% Rocío: This ref (https://www.nature.com/articles/d41586-020-01489-0 already in the .bib) can be cited for networking

@@

% Rocío: there's a link missing between this networking part and the paragraph above. This can go in a networking box.
Nevertheless, having a diverse offer of networking opportunities that can appeal to people with different backgrounds, accessibility needs, and preferences can be challenging, especially if you have the mindset of organizing each activity for the complete pool of attendants. If you think of smaller activities that can reach specific groups, preferably co-lead by community leaders, these sessions can be more productive and successful, and even inclusive, than trying to organize one single activity that can please the whole community. Some examples are the newbies sessions for first-timers, mixers lead by specific subgroups or communities, or leisure activities that reunite subgroups with the same interests: arts, exercise, sports, movies, etc.

%sara: agree that this fits better in the communication rule
Set the tone. %adding here from Liz's rule but maybe this could go in communication in general
In addition to excluding derogatory or discriminatory language, make the effort to teach yourself the vocabulary and the best ways to communicate to account for every culture and situation. Do not expect people to teach you --it's not their role-- and accept feedback without being defensive.

\section{Allocate financial resources to support the presence of diverse people in every space of the conference
}
\label{rule_financial}
%ast: new overall rationale (feel free to comment and change): conferences are expensive to organize and some work on limited budgets. this repercutes in fee costs -but fees for attendance are exclusionary- there should be fees, less no-shows. fees should be set fairly. 
%scholarships or grants to attend are a common way to boost participation from diverse groups but they attract people who believe they'll win -already privileged- people who do not need them but could use the prestige (for lack of another word) to fit in their cv, 
% Rocío: Rewrite as a design rule.
\subsection{Set fair registration rates and provide financial support when needed}
Conferences, even virtual ones, should have registration fees for two primary reasons. The first one is that preparing the conference involves a lot of concerted effort and costs money (e.g., commercial registration tools, captioning, or conference venue, if in-person) and this translates to the participation fee. The second reason has to do with psychology -- people value more the things they pay for, and there is a lower attendance rate for free events than for events with registration costs \cite{eventbrite_ultimate_2017}.

On the other hand, if we are aiming for inclusiveness and representation, the socioeconomic context of participants should be taken into account when determining the registration rates. Usually, there is a higher fee for people from the industry than for academia. A lower fee for non-profit organizations, government employees, or freelancers should also be considered. It is important to include discounts for students as well as for postdocs (early career researchers) to encourage their participation \cite{sarabipourChangingScientificMeetings2021, andalibPostdocQueueLabour2018, kaplanPostdocNot2012}. Since postdoc (or trainee) statuses are not always well-defined in academia and can vary for each country, their payment category should be explicitly defined. You can take into account the cost of living in each country using conversion factors (e.g. from the International Comparison Program report of the World Bank \cite{arendDisparityConferenceRegistration2019}). Consider that, while it is traditional for employers to provide --at least some --conference support in the Global North, this is not the case everywhere.

Offering scholarships or grants to attend the conference are a common way to boost participation from diverse groups, and some conferences ask for cover letters or applications  but they may be counterproductive, as they can be seen as more of a competition and attract people that might not need the money (e.g., when their PI could pay for it) but could apply for it to enrich their CV while filtering out people who do not feel entitled to earn them. If the goal is to help the people who really need it, the language needs to make that clear without shrouding it with fancy-sounding phrases or terms that single out the recipients (e.g. `grant recipient' or `diversity scholar', respectively). Do not call it a scholarship or a grant. Ultimately, it is a fee waiver or a discount for the people who need additional financial support. Also, the process for applicants should be simplified. Applying for loans, grants, and scholarships may be an emotionally demanding task. Do not complicate the attendees' lives by asking for long essays to convince a committee that they deserve your support. For this stage of the process, a certain degree of trust goes a long way -- when they say they need the support, it is best to give them the waiver rather than second guess their eligibility.

@@

\subsection{Do not expect the organizing team to work full time and for free}
\label{rule_pay_team}
Having a diverse team and executing inclusive and accessible practices throughout the organizing period --it might be a year or two --may require a lot of effort. The effort is worth it because it strengthens the event and the community making it truly welcoming for everyone. However, having a strong community as the only reward may be enough if you are in a privileged position. Some people and often the minoritized ones do not have institutional support to put time and effort into the organization tasks and do not have the luxury to commit to the organization for free. In addition, tasks such as taking and responding to code of conduct reports, can be emotionally intense work and should be additionally rewarded. Be mindful of each particular context, be flexible with hours or commitments, and revise your budget; if possible, secure funds to offer stipends to them early on.

>>>>

If the conference is in person, the venue must be accessible for people with mobility limitations. 
Accommodations such as a quiet space for neurodivergent people should also be provided.
Presenters should always speak into a microphone to make it easier for the hard of hearing and for captioners or interpreters to listen to them. 
Regardless of the conference format --online, in person, or hybrid --images used in communications about the conference should be accompanied by alternative text, while videos should have both captions and sound. 
Platforms for conference registration and abstract submission, websites, and chat platforms --if used --should be screen-reader friendly and keyboard accessible, with low technology requirements (hardware, software, and internet connection). 
Captioning for presentations should be available in more than one language if possible.
Do not forget about making your social events accessible (e.g. art shows and movies) and making sure that the materials presented are accessible for all. 
These aspects should be tested well in advance of going live.

@@

% Rocío: Pasting Batool's text in her 10 simple rules because there are very valuable things we could use: "Rule: Meeting the need of linguistically diverse audience. Most international conferences are held in English. However, English is only spoken by 4.83 percent of the world population. If the panellist or speakers will not be presenting in their native language, it may helpful to rephrase audience questions in a less complex language. Consider letting speakers know in advance that they can ask for a question to be translated to them in their native language and that they can respond in their native language.    If possible, ensure that some sessions are delivered by languages other than English"

\section{Express the welcoming spirit in your communication strategy}
\label{rule_communication}
%ast: sara mentioned something that can be good spirit for the communication rule: don't do anything to the outside that you are not doing for your team. it's communication strategy but also there should be coherence between your actions and your words. %Rocío: I love that. Please add it.

@@

@@

% Rocío: pasting this part of the text here because it may go under Andrea's idea for communication: "Nevertheless, having a diverse offer of networking opportunities that can appeal to people with different backgrounds, accessibility needs, and preferences can be challenging, especially if you have the mindset of organizing each activity for the complete pool of attendants. If you think of smaller activities that can reach specific groups, preferably co-lead by community leaders, these sessions can be more productive and successful, and even inclusive, than trying to organize one single activity that can please the whole community. Some examples are the newbies sessions for first-timers, mixers lead by specific subgroups or communities, or leisure activities that reunite subgroups with the same interests: arts, exercise, sports, movies, etc."

%sara: this fits better in the communication rule
Set the tone. %adding here from Liz's rule but maybe this could go in communication in general
In addition to excluding derogatory or discriminatory language, make the effort to teach yourself the vocabulary and the best ways to communicate to account for every culture and situation. Do not expect people to teach you --it's not their role-- and accept feedback without being defensive.

\section{Allocate financial resources to support the presence of diverse people in every space of the conference
}
\label{rule_financial}

%ast: new overall rationale (feel free to comment and change): conferences are expensive to organize and some work on limited budgets. this repercutes in fee costs -but fees for attendance are exclusionary- there should be fees, less no-shows. fees should be set fairly. 
%scholarships or grants to attend are a common way to boost participation from diverse groups but they attract people who believe they'll win -already privileged- people who do not need them but could use the prestige (for lack of another word) to fit in their cv,

\subsection*{Inclusion comes with a cost}

Many inclusive practices come with a cost and it is important to add them to the budget when planning the conference. 
Good quality and professional captioning, interpreters or translators, accessible and screen-reader friendly registration tools--and chat platform if the conference is online--, paying your organizing team (see \textbf{Rule \ref{rule_team}}), and code of conduct training, are of the some expenses that you may have to include in your budget. 
Budgets are limited, so it is important to estimate costs in advance and define your priorities.

\subsection*{Set fair registration rates and provide financial support when needed}

Conferences, even virtual ones, should have registration fees for two primary reasons. The first one is that preparing the conference costs money and this is likely to translate to the participation fee. The second reason has to do with psychology: people value more the things they pay for, and there is a lower attendance rate for free events than for events with registration costs \cite{eventbrite_ultimate_2017}.

On the other hand, if we are aiming for inclusiveness and representation, the socioeconomic context of participants should be taken into account when determining the registration rates. Usually, there is a higher fee for people from the industry than for academia. A lower fee for non-profit organizations, government employees, or freelancers should also be considered. It is important to include discounts for students to encourage their participation \cite{sarabipourChangingScientificMeetings2021, andalibPostdocQueueLabour2018, kaplanPostdocNot2012}. Since postdoc (or trainee) statuses are not always well-defined in academia and can vary for each country, they should be allowed to locate themselves in a category they consider affordable (i.e. student, researcher or `pay what you can'). To fix the registration costs, you can take into account the cost of living in each country using conversion factors (e.g. from the International Comparison Program report of the World Bank \cite{arendDisparityConferenceRegistration2019}). Consider that, while it is traditional for employers to provide--at least some--conference support in the Global North, this is not the case everywhere.

Offering scholarships or grants to attend the conference are a common way to boost participation from diverse groups, and some conferences ask for cover letters or applications  but they may be counterproductive, as they can be seen as more of a competition and attract people that might not need the money (e.g., when their PI could pay for it) but could apply for it to enrich their CV while filtering out people who do not feel entitled to earn them. 
Also, the process for applicants should be simplified. Applying for loans, grants, and scholarships may be an emotionally demanding task. Do not complicate the attendees' lives by asking for long essays to convince a committee that they deserve your support. For this stage of the process, a certain degree of trust goes a long way-- when they say they need the support, it is best to give them the waiver rather than second guess their eligibility. 
Only if the applicants for fee waivers are numerous and your budget cannot allow for that many fee waivers, you could ask for a short application. You could try to reduce this risk by finding enough sponsoring money so that you do not depend on registration fees to pay for your conference.

@@

% If the goal is to help the people who really need it, the language needs to make that clear without shrouding it with fancy-sounding phrases or terms that single out the recipients (e.g. `grant recipient' or `diversity scholar', respectively). Do not call it a scholarship or a grant. Ultimately, it is a fee waiver or a discount for the people who need additional financial support. 
% Rocío: I removed the part of naming the scholarship/grant/waiver, because if it goes somewhere it should be communication. Andrea, Batool, please see if it fits there.
